Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-13 paper/paper.tex
pass on eval

This section reports the results obtained with cross-engine differential
testing. More precisely, we report results obtained by fuzzing test
inputs, running those inputs on different engines, and checking the
outcomes with a differential oracle.

\vspace{0.5ex}
\subsubsection{Methodology}
The experimental methodology we used is as follows. As explained in
Section~\ref{sec:objects:fuzzers}, we used Radamsa~\cite{radamsa} and
QuickFuzz~\cite{quickfuzz} for fuzzing. To avoid experimental noise,
we only fuzz test files that pass in all engines--a total of
\totalTestFilesPassInAll\ tests satisfy this restriction. Those tests
appear under the column ``no-fail-in-all'' on
Table~\ref{tab:test-suites}.  We want to avoid the scenario where
fuzzing produces a fault-revealing input based on a test that was
already revealing failures on some engine. This decision facilitates
our inspection task; it helps us establish cause-effect relationship
between fuzzing and the observation of discrepancy.  We configured our
infrastructure (see Figure~\ref{fig:workflow}) to produce 20
well-formed fuzzed files per input file, \ie{}, the number of fuzzing
iterations can exceed the number above as we discard generated files
that are syntactically invalid.

@@

\vspace{0.5ex} \lbrack{}Exploratory Phase\rbrack{} For the first
three months of the study, our inspection process was exploratory.  In
this phase, we wanted to learn whether or not black-box fuzzers could
reveal real bugs and how effective was the \hi{}-\lo\ warning
classification.  We expected the number of warnings to increase
dramatically compared to the previous experiment and, if we realized
that the ratio of bugs from \lo\ warnings was rather low, we could
focus our inspection efforts on \hi\ warnings. To run this experiment,
we trained eight students in analyzing the warnings that our
infrastructure produces. The students were enrolled in a
graduate-level testing class. We listed warnings in a spreadsheet and
requested the students to update an ``owner'' column indicating who
was working on it, but we did not enforce a strict order on the
warnings the students should inspect. Recall from
Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
buckets. For that reason, we only listed one \lo\ warning per
representative class/bucket in the spreadsheet. First, we explained,
through examples, the possible sources of false alarms they could find
and then we asked the students to use the following procedure when
finding a suspicious warning. Analyze the parts of the spec related to
the problem and, if still suspicious, look for potential duplicates on
the bug tracker of the affected engine using related keywords. If none
was reported, indicate in the spreadsheet that that warning is
potentially fault-revealing. We encouraged students to use
lithium~\cite{lithium} to minimize long test cases\Comment{; the tests
  from the Mozilla suite are often longer than others}. A bug report
was filed only after one of the authors reviewed the diagnosis. Each
student found at least one bug using this methodology.

\vspace{0.5ex}
\lbrack{}Non-Exploratory Phase\rbrack{} Results obtained in the
exploratory phase confirmed our expectations that most of the bugs
found during the initial period of investigation were related to
\hi\ warnings. For that reason, we changed our inspection
strategy. This time, only the co-authors inspected the bugs using a
similar discipline as before. However, the set of warnings inspected
and the order of inspection changed. We restricted our analysis to
\hi\ warnings and, aware that we would be unable to analyze each and
every warning reported, we grouped those warnings per engine,
analyzing each group in a round-robin fashion.  At each iteration, we
analyzed \warningsIteration{} warnings in each group. A warning
belongs to the group of a given engine if only that engine manifests
distinct behavior, \ie{}, it produces a distinct output compared to
others. We separated in a distinct group the warnings for which two
engines diverge. The rationale for this methodology was to give
attention to each engine more uniformly, enabling more fair comparison
across engines.

@@

This section describes the experiment we conducted to evaluate the
effectiveness of the techniques we studied to find new bugs in
\hermes, a JavaScript engine that has started development very
recently. \hermes is a JavaScript engine introduced by Facebook in
2019. According to its website, \hermes is ``a JavaScript engine
optimized for fast start-up of React Native apps on
Android''~\cite{hermes2020repo}.\Mar{short sentence saying where it is
  used.}\Igor{Currently, hermes is being used in the react-native framework,
  also maintained by Facebook, as a beta component to increase the performance of Android applications,
  such as startup time, reduce memory consumption and application size\cite{reactnative2020hermes}.
}

@@

We followed the same methodology described in previous sections to
evaluate \hermes. When experimenting with test transplantation, we
noted many errors when replaying the test suite of \smonkey on
\hermes. This happened because \smonkey has its own assertion
framework, but \hermes was unable to interpret those assertions \Igor{due to 
the missing features mentioned before (\ie\ Class definitions, Proxy properties)}
resulting in failures in all test executions from this engine. These
failures did not happen when the \smonkey tests were transplanted to
the other engines, though.\Mar{Why? Was the framework using some of the
  features aforementioned? Say it, please}\Igor{fixed above}.
Overall, we reported three issues to the \hermes bug tracker as result of using test
transplantation\footnote{\url{https://github.com/facebook/hermes/issues/<id>},
  with id 265, 266, 267.}. One of them was confirmed by the \hermes
maintainers by the time of this submission. For another, the
maintainer explained the issue was related to a feature not yet
supported---a \texttt{return} statement outside the scope of a
block. For the third issue, developers disagreed on the proper
implementation of one particular part of the specification involved in
the issue (i.e., whether a numeric escape character (non-octal-eight,
\texttt{\textbackslash{8}}) should be allowed or not in strict
mode. The issue was closed, but the maintainers opened a new one to
discuss this matter. By following the discussion, it was interesting
to observe that maintainers are aware that this feature is implemented
by other engines such as \veight, \chakra, and \smonkey. Yet, they
were unsure how they should treat it in \hermes.  Considering
differential testing, we found and reported one bug on \hermes using
\radamsa. As of this writing, this particular bug report was not yet
addressed by any \hermes maintainer.

>>>>

This section reports the results obtained with cross-engine differential
testing.

%More precisely, we report results obtained by fuzzing test
%inputs, running those inputs on different engines, and checking the
%outcomes with a differential oracle.

%\vspace{0.5ex}
\subsubsection{Methodology}
The experimental methodology we used is as follows. As explained on
Section~\ref{sec:objects:fuzzers}, we used Radamsa~\cite{radamsa} and
QuickFuzz~\cite{quickfuzz} for fuzzing. To avoid experimental noise,
we only fuzz test files that pass in all engines--a total of
\totalTestFilesPassInAll\ tests satisfy this restriction. Those tests
appear under the column ``no-fail-in-all'' on
Table~\ref{tab:test-suites}.  We want to avoid the scenario where
fuzzing produces a fault-revealing input based on a test that was
already revealing failures on some engine. This decision facilitates
our inspection task; it helps us establish cause-effect relationship
between fuzzing and the observation of discrepancy.  We configured our
infrastructure (see Figure~\ref{fig:workflow}) to produce 20
well-formed fuzzed files per input file, \ie{}, the number of fuzzing
iterations can exceed the number above as we discard generated files
that are syntactically invalid.

@@

\vspace{0.5ex} \lbrack{}Exploratory Phase\rbrack{} For the first
three months of the study, our inspection process was exploratory.  In
this phase, we wanted to learn whether or not black-box fuzzers could
reveal real bugs and how effective was the \hi{}-\lo\ warning
classification.  We expected the number of warnings to increase
dramatically compared to the previous experiment and, if we realized
that the ratio of bugs from \lo\ warnings was rather low, we could
focus our inspection efforts on \hi\ warnings. To run this experiment,
we trained eight students in analyzing the warnings that our
infrastructure produced. The students were enrolled in a
graduate-level testing class. We listed warnings in a spreadsheet and
requested the students to update an ``owner'' column indicating who
was working on it, but we did not enforce a strict order on the
warnings the students should inspect. Recall from
Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
buckets. For that reason, we only listed one \lo\ warning per
representative class/bucket in the spreadsheet. First, we explained,
through examples, the possible sources of false alarms they could find
and then we asked the students to use the following procedure when
finding a suspicious warning. Analyze the parts of the spec related to
the problem and, if still suspicious, look for potential duplicates on
the bug tracker of the affected engine using related keywords. If none
was reported, indicate in the spreadsheet that that warning is
potentially fault-revealing. We encouraged students to use
lithium~\cite{lithium} to minimize long test cases\Comment{; the tests
  from the Mozilla suite are often longer than others}. A bug report
was filed only after one of the authors reviewed the diagnosis. Each
student found at least one bug using this methodology.

\vspace{0.5ex} \lbrack{}Non-Exploratory Phase\rbrack{} Results
obtained in the exploratory phase confirmed our expectations that most
of the bugs found during the initial period of investigation were
related to \hi\ warnings. For that reason, we changed our inspection
strategy. This time, some of the co-authors inspected the bugs using a
similar discipline as before. However, the set of warnings inspected
and the order of inspection changed. We restricted our analysis to
\hi\ warnings and, aware that we would be unable to analyze each and
every warning reported, we grouped those warnings per engine,
analyzing each group in a round-robin fashion.  At each iteration, we
analyzed \warningsIteration{} warnings in each group. A warning
belongs to the group of a given engine if only that engine manifests
distinct behavior, \ie{}, it produces a distinct output compared to
others. We separated in a distinct group the warnings for which two
engines diverge. The rationale for this methodology was to give
attention to each engine more uniformly, enabling more fair comparison
across engines.

@@

This section describes the experiment we conducted to evaluate the
effectiveness of the techniques we studied to find new bugs in
\hermes, a JavaScript engine that has started development very
recently. \hermes is a JavaScript engine introduced by Facebook in
2019. According to its website, \hermes is ``a JavaScript engine
optimized for fast start-up of React Native apps on
Android''~\cite{hermes2020repo}. Currently, \hermes\ is used as a beta
component of the react-native framework, which is also maintained by
Facebook. The goal of \hermes\ at Facebook is to increase the
performance of Android applications, such as startup time, to reduce
memory consumption and application size~\cite{reactnative2020hermes}.

@@

We followed the same methodology described in previous sections to
evaluate \hermes. When experimenting with test transplantation, we
noted many errors when replaying the test suite of \smonkey on
\hermes. This happened because \smonkey has its own assertion
framework, but \hermes was unable to interpret those assertions
(because of missing features), resulting in failures in all test
executions from. These failures did not happen when the \smonkey tests
were transplanted to the other engines, though.  Overall, we reported
three issues to the \hermes bug tracker as result of using test
transplantation\footnote{\url{https://github.com/facebook/hermes/issues/<id>},
  with id 265, 266, 267.}. One of them was confirmed by the \hermes
maintainers by the time of this submission. For another, the
maintainer explained the issue was related to a feature not yet
supported---a \texttt{return} statement outside the scope of a
block. For the third issue, developers disagreed on the proper
implementation of one particular part of the specification involved in
the issue (i.e., whether a numeric escape character (non-octal-eight,
\texttt{\textbackslash{8}}) should be allowed or not in strict
mode. The issue was closed, but the maintainers opened a new one to
discuss this matter. By following the discussion, it was interesting
to observe that maintainers are aware that this feature is implemented
by other engines such as \veight, \chakra, and \smonkey. Yet, they
were unsure how they should treat it in \hermes.  Considering
differential testing, we found and reported one bug on \hermes using
\radamsa. As of this writing, this particular bug report was not yet
addressed by any \hermes maintainer.
